Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models

### 2017-01-20 presentation/presentation.tex
Added first slide.
Added slides for the introduction.

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Part I}
\subsection{}
\begin{frame}{Motivation}
  \begin{itemize}

  \item {
  Item 1
  }

  \item {
  Item 2  
  }

  \item {
  Item 3
  }
  \end{itemize}

  \centering{\includegraphics[scale=0.30]{eq18}}
\end{frame}

\section{Part II}
\subsection{}

\section{Part III}
\subsection{}

>>>>

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}
\subsection{}
\begin{frame}{The complete market framework}
  \begin{itemize}

  \item {
  Results
  }
	\begin{enumerate}
		\item{
		Outcomes are efficient - there is no alternative in which all households can be made better off.
		}
		\item{
		These models do not produce any inequality in well-being for identical households starting from identical positions. 
		}
	\end{enumerate}

  \item {
  Limitations  
  }
	\begin{enumerate}
		\item{
Unrealistic assumption of full insurance.
		}
		\item{
Limitation in questions we can ask. Impossible to ask questions, where differences across people might affect macroeconomic outcomes.
		}
	\end{enumerate}

  \end{itemize}

\end{frame}

\begin{frame}{Heterogeneity in models}
  \begin{itemize}

  \item {
  Uninsured risk
  }
	\begin{enumerate}
		\item{
Introduction of idiosyncratic or uncorrelated risk among individuals.
		}
		\item{
Accompanied by incomplete markets.
		}
		\item{
In such an environment aggregate risk may create further differences across groups of people.
		}
	\end{enumerate}

\item{
Differences among decisionmakers.
}

  \end{itemize}
\end{frame}

\begin{frame}{Why these models?}
	\begin{itemize}

	\item {
	Why the Aiyagari Model? 
	}
	\begin{enumerate}
	\item {
Allows for the study of agents' savings behavior while facing idiosyncratic risk in an incomplete market framework, where only part of the risk is covered by, for instance, public institutions. 
	}
	\item {
How does the bahvior of selfinsured agents change when public insurance systems, such as UI, change? 
	}
	\item {
	How do these changes in behavior in turn affect the other economic variables?
	}
	\item {	
	When would agents prefer a change and when not? Do these changes affect different groups differently? 
	}	
	\end{enumerate}

	\end{itemize}

\end{frame}

\begin{frame}{Why these models?}
	\begin{itemize}

	\item {
	Why the Krussell Smith model? 
	}

	\begin{enumerate}

	\item {
Aggregate shocks might affect different groups in a contrasting manner.  
	}
	\item {
Helps to improve redistributional policy measures in business cycles.
	}

	\end{enumerate}

	\end{itemize}

\end{frame}

\section{The Aiyagari Model}
\subsection{Model Setup}

\begin{frame}{Why these models?}
	\begin{itemize}

	\item {
	Consumers 
	}

	\end{itemize}

\end{frame}

\subsection{Mechanics governing the model}

\section{Aggregate Uncertainty}
\subsection{}

\begin{frame}{Idiosyncratic Uncertainty}
	\begin{itemize}

	\item {
	Why the Aiyagari Model? - Explaining the 				differences from the Representative Agent Model.
	}
	\item {
	Model Mechanics - How does a change in 					idiosyncratic uncertainty affect the agents' behavior?
	}
	\item {
	What conclusions can we draw from such an analysis?
	}
	\item {
	Where are the model's limitations?
	}		
	\end{itemize}
	  \centering{\includegraphics[scale=0.30]{eq18}}

\end{frame}
